\newpage
\noindent
{\large\bf How to Contact Barobo}\\
\vspace*{-6pt}

\begin{tabular} {ll}
Mail & Barobo, Inc. \\
      &813 Harbor Blvd, Suite 335\\
      &West Sacramento, CA 95691-2201\\
Phone & + 1 916 596-3050\\
%Fax & + 1 530 297 7392 \\
Web &http://www.barobo.com\\
Email &info@barobo.com 
\end{tabular}
\index{copyright}

\vspace{12pt}
\noindent
Copyright \copyright 2012 by Barobo, Inc.
All rights reserved. \\
\today\\

\noindent
Permission is granted for users to make
one copy for their own personal use. Further reproduction,
or any copying of machine-readable files (including this one)
to any server computer, is strictly prohibited.\\


\noindent
Barobo, Inc. 
is the holder of the copyright to the Mobot software
and Mobot User's Guide
described in this document, including without limitation
such aspects of the system as its code, structure,
sequence, organization, 
programming language, 
header files, 
function and command files,
object modules,
static and dynamic loaded libraries 
of object modules,
compilation of command and library names, 
interface with other languages and object modules
of static and dynamic libraries.
Use of the system unless pursuant to the terms
of a license granted by Barobo or as
otherwise authorized by law is an infringement
of the copyright.\\

\noindent
{\bf 
Barobo, Inc.
makes no representations, expressed or implied, with respect
to this documentation, or the software
it describes, including without limitations, any implied
warranty merchantability or fitness for a particular
purpose, all of which are expressly disclaimed.
Users should be aware that included in the terms and conditions
under which  Barobo is willing to license the Mobot software
as a provision that
Barobo , and their distribution
%the author, Barobo , and their distribution
licensees, distributors and dealers shall in no event
be liable for any indirect, incidental or consequential
damages in connection with, 
or arising out of, the furnishing, performance,
or use of the Mobot software
and that liability for direct damages shall be limited
to the amount of purchase price paid for Mobot and Mobot software.\\

\noindent
In addition to the foregoing, users should recognize
that all complex software systems and their documentation
%contain errors and omissions. The aand uthor and Barobo
contain errors and omissions. Barobo
shall not be responsible under any circumstances
for providing information on or corrections to errors
and omissions discovered at any time in this documentation
or the software it describes,
even if Barobo has
%even if the author and Barobo have
been advised of the errors or omissions.\\
}


\noindent
Barobo, Mobot, iMobot, RobotController, BaroboLink, and SnapConnector
are either
registered trademarks or trademarks of Barobo, Inc.
in the United States and/or other countries.
Ch, ChIDE, and  SoftIntegration 
are trademarks of SoftIntegrtation, Inc.
Microsoft, MS-DOS, Windows, Windows 2000, Windows XP, 
Windows Vista, and Windows 7
are trademarks of Microsoft Corporation.
Linux is a trademark of Linus Torvalds.
Mac OS X and Darwin are trademarks of Apple Computers, Inc.
All other trademarks belong to their respective holders.
